Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-10 main.tex
Test
Macros file, plus some progress on NI definition

\documentclass[conference]{IEEEtran}
\newif\ifdraft \drafttrue
\newif\iftext \textfalse

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{cleveref}
\usepackage{xcolor}
\newcommand{\bcp}[1]{\ifdraft\textcolor{violet}{{[BCP:~#1]}}\fi}

% Notational conventions
\newcommand{\HIGH}{\textsc{h}}
\newcommand{\LOW}{\textsc{l}}
\newcommand{\OBS}{\textsc{obs}}
\newcommand{\HIDDEN}{\textsc{hidden}}
\newcommand{\word}{W}
\newcommand{\addr}{A}
\newcommand{\WORDS}{{\mathcal W}}
\newcommand{\reg}{R}
\newcommand{\REGS}{{\mathcal R}}
\newcommand{\mach}{M}
\newcommand{\MACHS}{{\mathcal M}}
\newcommand{\PC}[1]{\PCname(#1)}
\newcommand{\PCname}{\textsc{pc}}
\newcommand{\pol}{P}
\newcommand{\contour}{C}
\newcommand{\CONTOURS}{{\mathcal C}}
\newcommand{\component}{K}
\newcommand{\COMPONENTS}{{\mathcal K}}

\newcommand{\stepsto}{\Longrightarrow}
\newcommand{\stepstounder}[1]{\stackrel{\mbox{\tiny{$#1$}}}{\Longrightarrow}}
\newcommand{\stepstounderfull}{\stepstounder{\textsc{RISCV}}}
\newcommand{\manystepsto}{\stepsto^\star}
\newcommand{\obstrace}{\mathit{obstrace}}

\newcommand{\underscore}{\mbox{\_}}

@@

The {\em observation trace} arising from an infinite sequence of contours
and machine states $(\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots$,
written $\obstrace((\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots)$
 is
the (finite or infinite) sequence of {\em distinct} values taken on by the
{\em observable} components of each state.  \iftext\bcp{Give an example and
  write it out formally.}\fi \bcp{Question: This could be defined in two
  ways, and I'm not sure which is better or if it really matters: the
  observation trace is a sequence of partial maps from components to their
  values, or the observation trace is a partial maps from components to
  their sequences of observable values.  This starts getting a bit
  technically tangled, but I don't see a simpler alternative right now.
  Answer: map from components to sequences of words.}

@@

\bcp{Proposal: sequences of values of the observable locations are what gets
  compared.  Fix the following:}

If $\mach$ and $\mach'$ are variant machine states with respect to contour
$\contour$, then $\mach$ and $\mach'$ are said to be {\em indistinguishable}
under policy $\pol$ if either (1) one or both of $(\contour,\mach)$ and
$(\contour,\mach')$ fail to terminate when executed with
$\stepstounder{\pol}$, or (2) both terminate and the machine-state
components of their results are variants with respect to the original
$\contour$.

>>>>

\documentclass[conference]{IEEEtran}
\input{macros}

@@

The {\em observation trace} arising from a finite or infinite sequence of
contours and machine states
$(\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots$, written
$\obstrace((\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots)$ is a
partial map taking each machine component to the (finite or infinite)
sequence of {\em distinct} values taken on by this component at moments when
it is {\em observable}.  Formally, this map can be constructed as
follows. For each component $\component$,
%
(1) if
$\contour_i(\component) = (\underscore,\HIDDEN)$ for all $i$, then
$\obstrace(\component) = \bot$;
%
and otherwise (2), $\obstrace(\component)$ is a sequence whose first element
is $\mach_i(\component)$ for the smallest $i$ such that
$\contour_i(\component) = (\underscore,\OBS)$ and whose $(m+1)^{th}$ element
(if any) is $\mach_j(\component)$, where $j$ is the smallest index greater
than the index $i$ of the $m^{th}$ element and such that
$\contour_j(\component) = (\underscore,\OBS)$ and
$\mach_j(\component) \neq \mach_i(\component)$.
%
\iftext
\bcp{Unfinished and horrible...  But maybe the textual description is OK?}
\newcommand{\aux}{\mathit{aux}}
\bcp{Don't like the ``rest'' argument and the fact that we don't
  have a metavariable for sequences of pairs of contours and machines.
  Consider defining one.}
%
\[
\begin{array}{lcl}
\aux \; ( [\,] ) \; \trace& = & \trace
\\
\aux \; ( (\contour,\mach) \mathrel{::} \mathit{rest} ) \; T
  & = &
        \aux \;( \mathit{rest} )
        \\ && \quad (\lambda k.\; \mbox{\bcp{and so on}}
\\
\\
\obstrace \;( (\contour_0,\mach_0),\, \ldots )
  &=& \aux \; ( (\contour_0,\mach_0),\, \ldots ) \; (\lambda
      \component.\, \bot)
\end{array}
\]
\fi

@@

\bcp{I'm confused here about policy vs. property -- e.g., which contours are
  requirements and which are chosen by the micropolicy.}

If $\mach$ and $\mach'$ are variant machine states with respect to contour
$\contour$, then $\mach$ and $\mach'$ are said to be {\em indistinguishable}
under policy $\pol$ if their observable
%
$\obstrace(
                      (\contour,\mach)
  \stepstounder{\pol} (\contour_1,\mach_1)
  \stepstounder{\pol} (\contour_2,\mach_2)
  \stepstounder{\pol} \ldots)$
%
yields the same trace as
$\obstrace(
                      (\contour,\mach')
  \stepstounder{\pol} (\contour_1,\mach_1')
  \stepstounder{\pol} (\contour_2,\mach_2')
  \stepstounder{\pol} \ldots)$.

% either (1) one or both of $(\contour,\mach)$ and
% $(\contour,\mach')$ fail to terminate when executed with
% $\stepstounder{\pol}$, or (2) both terminate and the machine-state
% components of their results are variants with respect to the original
% $\contour$.
